path-independence

### 2020-03-08 main.tex
idk

Every element in the output of the path extraction algorithm was by definition a conflicting pair.

It remains to show that every new conflicting pair corresponds to a two flip tolerant path. Let the common source be $F_1$ and common sink be $F_2$. 
Note that we are excluding pair where both paths include the new edge, since such paths are equal from $F_1$ to S because of the path independence of the original graph, identical from S to T, and again equal from T to $F_2$ because of original path independence. Being the composition of equal parts, these paths must always be equal.

@@

@@

\paragraph{Theorem} This reduction rule is the most general possible.
\paragraph{Proof} TODO write. Basically we create an axiom set where the only allowed action is composing with functions. This leads to only one inference rule to show implication between path equalities. We show that to derive p1>p2 using the inference rule some number of times, it is necessarily true that p1 and p2 have the relationship described in this case.

>>>>

Every element in the output of the path extraction algorithm was by construction a conflicting pair.

It remains to show that every new conflicting pair corresponds to a two flip tolerant path. Let the common source be $F_1$ and common sink be $F_2$. 
Note that we are excluding pair where both paths include the new edge, since such paths are equal from $F_1$ to S because of the path independence of the original graph, identical from S to T, and again equal from T to $F_2$ because of original path independence. Being the composition of equal parts, these paths must always be equal.
Further, we are excluding pairs where one of the paths contains a cycle that excludes the new edge, because again the path independence of the original graph implies that the path with the cycle must be equal to the path with the cycle removed.

@@

The special case is that of cycles, where path 1 corresponds to some cycle in the graph that excludes the new edge and path 2 is a cycle that includes the new edge.
Path 2 corresponds to a path with 0 flips that is caught by the two-flip tolerant algorithm. Subsequently the path extraction algorithm finds path 1 and generates the pair of path 1 and path 2.

We have shown that all paths that need verification are caught by the two flip tolerant search followed with path extraction.

@@

\paragraph{Theorem} This reduction rule is the most general possible.
\paragraph{Proof} TODO write. Basically we create an axiom set where the only allowed action is composing with functions. This leads to only one inference rule to show implication between path equalities. We show that to derive p1$>$p2 using the inference rule some number of times, it is necessarily true that p1 and p2 have the relationship described in this case.
